Statistically-estimated tree composition for the northeastern United States \\ at the time of Euro-American settlement

### 2016-02-03 plos_revision/coverLetter.tex
revised and added for plos revision january 2016

\documentclass[12pt]{letterhead_stat}
\usepackage{graphicx}
\special{papersize=8.5in,11in}
\textwidth=6.5in
\textheight=8.5in
\parindent=0.0cm
\parskip=0.4cm
\oddsidemargin=0.0in
\evensidemargin=0.0in
\topmargin=-0.594in
\begin{document}
\telephone{(510) 642-6190\\
E-mail: paciorek@stat.berkeley.edu\\
fax: (510) 642-7892}
\name{Christopher Paciorek}
\signature{\vspace{-2em}\hspace{-.3cm}\includegraphics[height=.6in,width=2in]{goodSignature.jpg}\\Christopher Paciorek\\Associate Research Statistician\\Department of Statistics\\University of California, Berkeley}
\begin{letter}{\mbox{}}
\opening{To whom it may concern,}

Please consider our submission as a research article.

This submission presents a new statistically-derived data product and the methods used to create the product. The product provides an estimate of forest composition, with uncertainty, for much of the northeastern United States at the time of European settlement. As such, it is valuable resource for ecologists and for climate change work as it provides baseline information about forests before widespread European land use change.

The raw data underlying this product have not been collected and made available in one place to date as they represent the work of a number of researchers and in some cases data are still unpublished. Our product provides a publicly available resource.

With regard to possible editors, either someone with expertise in statistics applied to environmental applications or someone with expertise in biogeography or landscape-scale ecology would be appropriate. There are a number listed on your website with expertise in biogeography, community ecology, global change ecology, or spatial and landscape ecology. In terms of editors with expertise in statistics, potential editors include Alex Cook, Thomas Nichols, Nicholas Reich.

>>>>

\documentclass[12pt]{letterhead_stat}
\usepackage{graphicx}
\special{papersize=8.5in,11in}
\textwidth=6.5in
\textheight=8.5in
\parindent=0.0cm
\parskip=0.4cm
\oddsidemargin=0.0in
\evensidemargin=0.0in
\topmargin=-0.594in
\begin{document}
\telephone{(510) 642-6190\\
E-mail: paciorek@stat.berkeley.edu\\
fax: (510) 642-7892}
\name{Christopher Paciorek}
\signature{\vspace{-2em}\hspace{-.3cm}\includegraphics[height=.6in,width=2in]{goodSignature.jpg}\\Christopher Paciorek\\Associate Research Statistician\\Department of Statistics\\University of California, Berkeley}
\begin{letter}{\mbox{}}
\opening{Dear Editor,}

We are responding to reviewer comments for PONE-D-15-41521.

Thank you for your consideration of our manuscript.
